Analysis paper

### 2021-05-02 analysis/analysis.Rmd
add daily truth data and save table as png

@@

  # add an empty line to data.frame to separate deaths and cases
  table <- 
    rbindlist(list(
    scores[1:4], 
    as.list(rep(NA, ncol(scores))), 
    scores[5:9]
  )) %>%
    kable(format = "markdown") %>%
    kable_styling(bootstrap_options = "striped")
  return(table)
}
```

@@

eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
  make_score_table()
```

>>>>

## Visualsiation of daily data

```{r}
dailytruth_data %>%
  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
                target_end_date <= max(forecast_dates$full_hub_period)) %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_point() + 
  geom_line() + 
  facet_grid(target_type ~ location_name, scales = "free")

ggsave(here("analysis", "plots", "daily_truth.png"))
```

@@

  # add an empty line to data.frame to separate deaths and cases
  table <- 
    rbindlist(list(
    scores[1:4], 
    as.list(rep(NA, ncol(scores))), 
    scores[5:9]
  )) %>%
    kable() %>% #format = "markdown"
    kable_styling(bootstrap_options = "striped")
  return(table)
}
```

@@

table <- eval_forecasts(
  data[grepl("2", target)], 
  summarise_by = c("model", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "target_type")) %>%
  make_score_table()

save_kable(table, file = here("analysis", "plots", "table_scores_2_ahead.png"))
